AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
todo to discuss CIA.vc bots
figsize aspectratio fixed
improved 1st paragraph

One of the defining features of modern times is the widening
geographical distribution of software teams~\cite{last2003} creating
what is called Global Software Development (henceforth
GSD)~\cite{german2003}. An example is the free software
movement. Projects and institutions like Mozilla Foundation has many
employees and thousands of voluntary developers distributed around
many countries. The same is true for GNOME~\cite{german2003}, OpenBSD,
MySQL or Apache Software Foundation, to enumerate just the most active
projects\footnote{Ohloh, the open source network, have a more complete
  and constantly updated list of the most active projects on-line at
  \url{http://www.ohloh.net/}}. Along the free and open software
projects, GSD is growing popularity in every niche of software
industry as a whole, even on those distributing their software with
proprietary licenses. This phenomenon is attributed to various factors
like larger labor pool, natural globalization of software companies
and foundations or even the premise of cheaper cost of
production~\cite{komi2005}.

@@

@@

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-0_1.png}
\end{center}
   \caption{AA Version 0.1}
\label{fig:aaserver}
\end{figure}

@@

We would like to also thanks AA: this whole research and even this
paper was written using AA. The complete log is on-line at
\url{http://hera.ethymos.com.br:1080/paainel/casca/}.

>>>>

One of the defining features of modern times is the widening
geographical distribution of software teams~\cite{last2003} creating
what is called Global Software Development (henceforth
GSD)~\cite{german2003}. An example is the free software
movement. Projects and institutions like Mozilla Foundation has several
employees and thousands of voluntary developers distributed across
many countries. The same is true for GNOME~\cite{german2003}, OpenBSD,
MySQL or Apache Software Foundation, to cite just a few of the most active
projects.\footnote{Ohloh, the open source network, have a more complete
  and constantly updated list of the most active projects on-line at
  \url{www.ohloh.net}} Along the free and open software
projects, GSD is growing popularity in every niche of the software
industry as a whole, even on those distributing their software with
proprietary licenses. This phenomenon is attributed to a variety of factors
such as a larger labor pool, natural globalization of software companies
and foundations or even the premise of cheaper cost of
production~\cite{komi2005}.

@@

\indraftnote{TODO: cite CIA.vc bot stuff}

@@

\begin{figure}
\begin{center}
   \includegraphics[width=0.95\linewidth]{figs/aa-0_1.png}
\end{center}
   \caption{AA Version 0.1}
\label{fig:aaserver}
\end{figure}

@@

We would like to also thank AA: the present research and even this
manuscript was written using AA. The complete log is on-line at
\url{http://www.pulapirata.com/skills/aa}.
